Draft information

### 2019-05-06 paper/draft-info.Rmd
Updated draft changes

* Added .git and .drake to .dockerignore to speed up build

>>>>

* Added .git and .drake to .dockerignore to speed up build
* As suggested by Jason I refer to the factors on the main models as mechanisms of pollinator mediated competition. 
* Many minor changes to the text
* Replaced instances of "plant abundance" to the more specific term "floral abundance" (Jamie suggested some people working in the field might be finicky with terminology).
